---
title: "data_challenge"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidycensus)
library(sf)

library(tigris)

library(stringr)
library(censusapi)
library(ggthemes)
library(leaflet)
library(janitor)
library(mapview)
```


```{r}
# 19v1
data <- read_csv("C:/Users/aslop/Desktop/Data challenge/PLUTO subset CUNY data challenge - pluto_datachallenge_subset.csv")
glimpse(data)
```

```{r}
head(data)

```

Using the above PLUTO data and the software of your choice, create a map illustrating
the number residential units for lots where the assessed total value is $1,000,000 or
more. If you create a static map, please deliver your map as a pdf; however, if you
create a web map please provide the link to your map in the answers.pdf file.

```{r}
# unitsres - The sum of residential units in all buildings on the tax lot.
# assesstot - The assessed total value for the tax lot

# filter lots with total value greater $1,000,000, create id

data_1 <- data %>% 
 filter(assesstot >= 1000000)%>%  
 select(unitsres, assesstot, bbl) 

```

```{r}
# download PLUTO shapefile
pluto_geo <- read_sf("C:/Users/aslop/Desktop/Data challenge/nyc_mappluto_19v1_arc_shp/MapPLUTO.shp")

pluto_geo_1 <- pluto_geo %>% 
 select(geometry, BBL)
```

```{r}
joined <- data_1 %>% 
  left_join(pluto_geo_1, by = c("bbl" = "BBL")) %>% 
  st_sf(crs = 2263)

class(joined)

st_crs(joined)
```

```{r}
# nyc community districts
cd <- read_sf("C:/Users/aslop/Desktop/Data challenge/nycd_19d/nycd_19d/nycd.shp")

cd_1 <- cd %>% 
  st_sf(crs = 2263)

st_crs(cd_1)
```


```{r}
joined_2 <- st_transform(joined, "+proj=longlat +ellps=WGS84 +datum=WGS84")

pal <- colorNumeric(palette = "Blues", domain = c(min(joined_2$unitsres), max(joined_2$unitsres)), na.color = "grey")


popup <- paste(sep = "<br/>", 
               paste0("<b>Residential units: </b>", joined_2$unitsres), 
               paste0("<b>Lot total value: </b>", joined_2$assesstot))


leaflet(joined_2, options = 
            leafletOptions(dragging = FALSE,
                           minZoom = 10, 
                           maxZoom = 15)) %>%
addProviderTiles("CartoDB.Positron") %>%
addPolygons(group = "continuous",
            stroke = TRUE, 
            smoothFactor = 0.5, 
            fillOpacity = 1,
            weight = 0.5,
            fillColor = ~pal(unitsres),
            popup = popup) %>% 
addLegend(position = "topleft", pal = pal, values = joined_2$unitsres,
          title = "Residential units",
          opacity = 0.6) 
```

3. Which record is the largest tax lot? How many buildings are on this tax lot? 

```{r}
data %>% select(lotarea, bbl, numbldgs) %>% 
  arrange(desc(lotarea))
```

4. How many unique building classes are in this dataset? 

```{r}
data %>% select(bldgclass) %>% unique() %>% count()
```

5. What is the most frequent land use type? 

```{r}
data %>% select(landuse) %>% 
  mutate(num = 1) %>%  
  group_by(landuse) %>% 
  summarise(sum = sum(num))
```

